An Embedding Framework for Consistent Polyhedral Surrogates

### 2021-06-01 poly-embed-journal/poly-embed-journal.tex
Sec 5: Commenting out old proofs, using PDs for property TFAE, and changed up proof for Prop 7 since it was using a lot of old results

\jessie{What is the relationship between minimum representative set non-redundancy.  At the end, want nice corollary about implication for embedding.}
\jessie{How do we want to think about finiteness here? Just assume it? }

@@

\begin{proposition}\label{prop:tfae-min-rep-nonredundant}
  Let $\R^*$ be a finite representative set for $L$ eliciting $\Gamma$.
  The following are equivalent:
  \begin{enumerate}
  \item[a.] $\R^*$ is a minimum representative set for $L$.
  \item[b.] $L|_{\R^*}$ is non-redundant.
  \item[c.] For all $r \in \R^*$, $\Gamma_r$ is full-dimensional and there is no $r' \in \R^*$ such that $\Gamma_{r'}= \Gamma_r$, and $\cup_{r\in\R^*} \Gamma_r = \simplex$.\jessie{Remove from here and bring back for property discussion?}
  \end{enumerate}
\end{proposition}
\begin{proof}[Sketch]
  $(a \implies b)$  
  We show the contrapositive: suppose $L|_{R^*}$ is redundant.
  Then there is a $r,r' \in \R^*$ such that $\Gamma_r \subseteq \Gamma_{r'}$.
  Then for all $p \in \Gamma_r$, we have $\{r, r'\} \subseteq \Gamma(p)$.
  Therefore, $\R^* \setminus \{r\}$ still a representative set, so $\R^*$ is not minimum.

  $(b \implies c)$
  If $L|_\R$ is non-redundant, then for all $r \in \R$, there is no $r'$ so that $\Gamma_r \subseteq \Gamma_{r'}$.
  This means the multiset $\{\Gamma_r : r \in \R\}$ contains no duplicate elements, since it has duplicate elements if and only if $\Gamma_r = \Gamma_{r'}$.
  Moreover, each $\Gamma_r$ is full-dimensional, since if there was a $\Gamma_r$ that was lower dimensional, it would have to be a subset of another level set, which would contradict non-redundancy. \jessiet{Hand waving here}
  Finally, we have $\cup_{r \in \R} \Gamma_r = \simplex$ since $\R$ is representative.

  $(c \implies a)$
  As $\Gamma_r$ is full-dimensional and there are no $r, r' \in \R$ such that $\Gamma_r = \Gamma_{r'}$, for each $r \in \R$ there must be some distribution $p_r \in \simplex$ so that $\Gamma(p_r) = \{r\}$.
  Thus, $\R \setminus \{r\}$ not a representative set for all $r \in \R$.
  Therefore, $\R$ is minimum.

  $(b \implies a)$
  Since $\R^*$ is finite, it suffices to show that for all $r \in \R^*$, there exists some $p_r \in \simplex$ such that $\{r\} = \Gamma(p_r)$.
  This implies the result, as removing $r$ from $\R^*$ would make $\Gamma(p_r) = \emptyset$, and therefore $\R^* \setminus \{r\}$ would not be representative.

  If there was an $r \in \R^*$ such that there was no such $p_r$, but $\Gamma_r \not \subseteq \Gamma_{r'}$ for any other $r' \in \R^*$, then we must have some $r', r''$ such that there exists a $p_{r'}^r$ and $p_{r''}^r$ such that $\{r,r'\} \subseteq \Gamma(p_{r'}^r)$ and $r'' \not \in p_{r'}^r$, and similarly, $\{r, r''\} \subseteq \Gamma(p_{r''}^r)$ and $r' \not \in \Gamma(p_{r''}^r)$.

  Observe that the hyperplane $H_L(p; u) := p \mapsto \inprod{p}{L(u)}$ supports $\risk{L}$ at $p$ if and only if $r \in \Gamma(p)$.
  By assumption, we have $H_L(p_{r'}^r; r)$ supporting $\risk{L}(p_{r'}^r)$ and $H_L(p_{r''}^r; r)$ supporting $\risk{L}(p_{r''}^r)$.
  As $H_L(\cdot;r)$ is linear in its first argument (this is true for any $r \in \R^*$), then $\risk{L}$ must be linear between $p_{r'}^r$ and $p_{r''}^r$.

  Now observe that 
  $r' \in \Gamma(p_{r'}^r) \iff H_L(p_{r'}^r; r')$ supports $\risk{L}(p_{r'}^r)$.
  Since $\risk{L}$ is linear between $p_{r'}^r$ and $p_{r''}^r$, \jessie{THIS IS INCORRECT} it therefore also supports $\risk{L}(p_{r''}^r) \iff r' \in \Gamma(p_{r''}^r)$, yielding a contradiction.

  Therefore, for all $r \in \R^*$, there must be some $p_r$ such that $\Gamma(p_r) = \{r\}$, and thus $\R^*$ is a minimum representative set.

  %	Observe that the hyperplane $H_L(p_{r'}^r; r) := p_{r'}^r \mapsto \inprod{p_{r'}^r}{L(r)}$ supports $\risk{L}$ at $p_{r'}^r$ if and only if $r \in \Gamma(p_{r'}^r)$.
  %	Similarly, we can conclude $H_L(p_{r''}^r; r)$ supports $\risk{L}$ at $p_{r''}^r$.
  %	However, $H_L(p_{r'}^r; r'')$ does not support $\risk{L}$ at $p_{r'}^r$, so we have
  %	\begin{align*}
  %   \inprod{p_{r'}^r}{L(r)} &= \inprod{p_{r'}^r}{L(r')} \neq \inprod{p_{r'}^r}{L(r'')}\\
  %   \inprod{p_{r''}^r}{L(r)} &= \inprod{p_{r''}^r}{L(r')} \neq \inprod{p_{r''}^r}{L(r'')}
  %	\end{align*}
  %	However, this yields a contradiction since $H_L(\cdot; r)$ is linear in its first argument, and therefore $\risk{L}$ must be linear between $p_{r'}^r$ and $p_{r''}^r$.
  %%	This means that each $\Gamma_r \subseteq \Gamma_{r'}$ or $\Gamma_{r''}$; in either case, we contradict non-redundancy.
  %%	\jessie{This is not well-written... nor correct as written?}

  $(a \implies c)$
  The level sets being full-dimensional follows from closure of level sets.
  No duplicate level sets follows from minimum representative sets, and union to the simplex follows from $\R^*$ representative.
\end{proof}

@@

\begin{remark}\label{remark:embed-trim}
  Let $\Gamma:\simplex\toto \R$ be an elicitable property.
  The following are equivalent:
  \begin{enumerate}\setlength{\itemsep}{0pt}
  \item $\Gamma$ embeds a finite property $\gamma:\simplex \toto \R'$.
  \item $\Gamma$ has a finite representative set $\U$.\jessie{, and therefore any minimum representative set for $\Gamma$ is also finite.}
  \item There is a finite multiset $\Theta$ full-dimensional level sets of $\Gamma$, and $\cup\, \Theta = \simplex$. 
  \end{enumerate}
  Moreover, when $\Gamma$ tightly embeds $\gamma$, $\U$ is a minimum representative set, and there is a $\Theta' \subseteq \Theta$ with no duplicate elements such that $\cup \Theta' = \simplex$.
\end{remark}
\begin{proof}[Sketch]
  $(a \implies b)$
  If $\Gamma$ embeds $\gamma$, then we can take the embedded target reports $\U := \varphi(\R')$ and show this is a finite representative set for $L$.
  We know it is finite as $\R'$ is finite, and consider that $\Gamma_{\varphi(r)} = \gamma_r$ for all $r \in \R'$, hence $\R \cap \gamma(p) \neq \emptyset \implies \varphi(\R) \cap \Gamma(p) \neq \emptyset$ for all $p \in \simplex$.

  $(b \implies c)$
  Consider that if $\U$ is a finite representative set for $L$, then $L$ has a finite minimum representative set $\U' \subseteq \U$.
  We have $\Theta := \trim(\Gamma) = \{\Gamma_u \mid u \in \U'\}$.
  This is finite as $\U'$ is finite, and unions to the simplex by $\U'$ being representative.
  If there was a level set $\Gamma_u$ for some $u \in \varphi(\R')$ that was not full-dimensional, it would have to be a subset of some other level set $\Gamma_{u'}$, but this contradicts that $\U'$ is minimal. \jessie{Hand waving; make the argument you can't span relints of other level sets.}

  $(c \implies a)$ 
  For each $\theta \in \Theta$, there is some $u \in \R$ so that $\theta = \Gamma_u$; take $\U'$ to be the set of such $u$s.
  We can see $\R'$ is representative since $\cup_{u \in \R'} \Gamma_u = \cup \theta = \simplex$, and therefore we have the result by an analog of Corollary~\ref{cor:representative-embeds-restriction}.

  % tight version; commented out May 8, 2021
  % $(a \implies b)$
  % If $\Gamma$ tightly embeds $\gamma$, then we can take the embedded target reports $\U := \varphi(\R')$ and show this is a finite minimum representative set for $L$.
  % We know it is finite as $\R'$ is finite, and consider that $\Gamma_{\varphi(r)} = \gamma_r$ for all $r \in \R'$.
  % If $\U$ was not minimum, then there would be some $r \in \R'$ so that $\U \setminus \{\varphi(r)\}$ is still representative.
  % This is true if and only if $\R' \setminus \{r\}$ is still representative for $\ell$, which contradicts non-redundancy of $\ell$ by tight embedding (Prop~\ref{prop:tfae-min-rep-nonredundant}).
  % Therefore, $\U$ is a finite minimum representative set for $L$.
  % 
  % $(b \implies c)$
  % We have $\trim(\Gamma) = \{\Gamma_u \mid u \in \varphi(\R')\}$, and take $\Theta := \trim(\Gamma)$.
  % This is finite as $\varphi(\R')$ is finite, and unions to the simplex by $\varphi(\R')$ being representative.
  % If there was a level set $\Gamma_u$ for some $u \in \varphi(\R')$ that was not full-dimensional, it would have to be a subset of some other level set $\Gamma_{u'}$, but this contradicts that $\varphi(\R')$ is minimal. \jessie{Hand waving; make the argument you can't span relints of other level sets.}
  % 
  % 
  % $(c \implies a)$ \jessie{Not quite: we need the multiset to have no duplicate elements}
  %% If we show $ c \implies b$, we have $b \implies a$ as an version of Corollary~\ref{cor:representative-embeds-restriction}.
  % For each $\theta \in \Theta$, there is some $u \in \R$ so that $\theta = \Gamma_u$; take $\R'$ to be the set of such $u$s.
  % If $\R'$ is a minimum representative set, then we have the result by an analog of Corollary~\ref{cor:representative-embeds-restriction}.
  % 
  % We can see $\R'$ is representative since $\cup_{u \in \R'} \Gamma_u = \cup \theta = \simplex$, and it is minimum since the multiset of $\Theta$ has no duplicate elements.
  % As the level sets are full-dimensional, each level set $\Gamma_u$ has some $p_u$ such that $\Gamma(p_u) = \{u\}$, so removing any $u$ from $\R'$ would make $\R'$ not representative.	
\end{proof}

\bigskip
\hrulefill

@@

@@

@@

@@

@@

\begin{proposition}\label{prop:embed-trim}
  Let $\Gamma:\simplex\toto\reals^d$ be an elicitable property.
  The following are equivalent:
  \begin{enumerate}\setlength{\itemsep}{0pt}
  \item $\Gamma$ embeds a finite property $\gamma:\simplex \toto \R$.
  \item $\trim(\Gamma)$ is a finite set, and $\cup\,\trim(\Gamma) = \simplex$.
  \item $\U$ is a finite minimum representative set for $\Gamma$.
  \item There is a finite set of full-dimensional level sets $\Theta$ of $\Gamma$, and $\cup\,\Theta = \simplex$.
  \end{enumerate}
  % \raft{I see why you wanted this addition here, but (a) it's clear from the def of embedding, and (b) we don't have varphi defined.  So let's leave it out.}
  Moreover, when any of the above hold, $\trim(\gamma) = \trim(\Gamma) = \{\Gamma_u : u\in\U\} = \Theta$, and $\gamma$ is elicitable.
\end{proposition}
\begin{proof}
  Let $L$ elicit $\Gamma$.

  1 $\Rightarrow$ 2:
  % \jessie{Loss intuition: Let $L$ elicit $\Gamma$.  If $\Gamma$ embeds a finite $\gamma'$, $L$ must embed a discrete loss $\ell$ such that $\ell(r) = L(\varphi(r))$.  Therefore, $\risk{L} = \risk{\ell}$ is polyhedral. Moreover, we have $\Gamma$ also embedding the finite property $\prop{\ell} := \gamma$ as a corollary of the definition of embedding properties. We claim $\trim(\Gamma) = \{\gamma_r : r \in \R\}$ (Lemma~\ref{lem:embedded-level-sets-trim}), and since the latter set is finitely generated (as $\R$ is finite), we have have $\trim(\Gamma)$ is finite.  Moreover, as $\gamma$ is nondegenerate (since it is defined over the simplex), we have that $\cup_{r \in \R} \gamma_r = \simplex$.}
  If $\Gamma$ embeds a finite $\gamma$, then Lemma~\ref{lem:embed-defs-equiv} says there is a discrete loss $\ell$ embedded by $L$ such that $\ell$ elicits $\gamma$.
  \raft{Again, a bit too brief.  Consider adding some of this statement into the Lemma. \jessie{Is this better?}}
  By Lemma~\ref{lem:embedded-level-sets-trim}, we then observe that there is a minimal representative set $\Sc$ such that $\trim(\Gamma) = \{\Gamma_{\varphi(r)} : r \in \Sc \} = \{\gamma_r : r \in \Sc\}$.
  As $\R$, and therefore $\Sc$ is finite, we conclude that $\trim(\Gamma)$ is also finite.
  % Since the latter set is finitely generated (as $\R$ is finite), we have have $\trim(\Gamma)$ is finite.
  Moreover, as $\gamma$ is nondegenerate (recall that $\gamma: \simplex \toto \R$ is shorthand for $\gamma: \simplex \to 2^\R \setminus \{\emptyset\}$ and $\Sc$ is representative), we have that $\cup \trim(\Gamma) = \cup_{r \in \Sc} \gamma_r = \simplex$, since if this were not true, $\Sc$ would not be a representative set for $\gamma$.

  \raft{These next two directions together seem like what we did before for $2\Rightarrow 3$, correct?  (Not as complete though; see the step where we justify the conditions of Lemma~\ref{lem:loss-restrict}.)  I'm actually happy for them to be separated, but let's make sure the argument is just as complete. \jessie{Added in the conditions of Lemma 3 to be a bit more thorough.}}
  2 $\Rightarrow$ 1:
  As $\trim(\Gamma)$ is finite, we know $\trim(\Gamma) = \{\Gamma_{u_i}\}_{i=1}^k$ for some finite $k$.
  Take $\U = \{u_1, \ldots, u_k\}$, and consider $L$ eliciting $\Gamma$ and $\ell := L|_{\U}$.  
  We have $\U \subset \reals^d$ and $\Gamma(p) \cap \U \neq \emptyset$ for all $p$, since we have $p \in \Gamma_{u_i}$ for some $u_i \in \U$.
  Then we can apply Lemma~\ref{lem:loss-restrict} to observe that $L$ embeds $\ell$, and therefore $\Gamma$ embeds $\prop{\ell}$, which is finite as $\ell$ is discrete and never empty.

  1 $\Rightarrow$ 3: 
  Let $\varphi: \R \to \reals^d$ be the embedding function, and take $\Theta = \{\Gamma_{\varphi(r)} : r \in \R\}$.
  The latter set is equal to $\{\gamma_r : r \in \R\}$ by Lemma~\ref{lem:embedded-level-sets-trim}.
  Therefore, we know each $\theta \in \Theta = \gamma_r$ for some $r \in \R$, which is full-dimensional in the affine hull of the simplex.
  Moreover, since $\gamma$ is non-degenerate, we have $\cup \Theta = \cup_r \gamma_r = \simplex$.
  %	\hrule
  %	Since $\Gamma$ embeds the finite property $\gamma$, Lemma~\ref{lem:embed-defs-equiv} yields a loss $\ell$ eliciting $\gamma$ embedded by $L$, and therefore $\risk{L} = \risk{\ell}$.
  %	As in the proof of Proposition~\ref{prop:embed-bayes-risks}, we observe that every facet of the epigraph of $-\risk{\ell}$ projects onto the simplex as a full-dimensional level set of $\gamma$.
  %	As the risks are equal, this is also true for $\Gamma$.
  %	Observe each cell in the simplex of $\gamma$ has some report $r$ so the cell is $\gamma_r$.
  %	If $\varphi: r \mapsto u_r$, then we must have $\gamma_r = \Gamma_{u_r}$.
  %	Take $\Theta$ to be the set $\{\Gamma_{u_r} : u_r \in \varphi(\R)\}$.
  %	We have shown each $\Gamma_{u_r}$ is full-dimensional, and as the union of these cells forms a power diagram on $\simplex$, we have $\cup \Theta = \simplex$.

  3 $\Rightarrow$ 1: \jessie{Intuition: Take $\gamma : p \mapsto \Gamma(p) \cap \varphi(\R)$.}
  Let $\Theta = \{\theta_1,\ldots,\theta_k\}$.
  For all $i\in\{1,\ldots,k\}$ let $u_i\in\reals^d$ such that $\Gamma_{u_i} = \theta_i$.
  Now define $\gamma:\simplex\toto\{1,\ldots,k\}$ by $\gamma(p) = \{i : p\in\theta_i\}$, which is non-degenerate as $\cup\,\Theta = \simplex$.
  By construction, we have $\gamma_i = \theta_i = \Gamma_{u_i}$ for all $i$, so letting $\varphi(i) = u_i$ we satisfy the definition of embedding, namely statement (i.).

>>>>

\jessie{How do we want to think about finiteness here? Just assume it? }

@@

\begin{proposition}\label{prop:tfae-min-rep-nonredundant}
  Let $\U$ be a finite representative set for $L$ eliciting $\Gamma$.
  $\U$ is a minimum representative set for $L$ if and only if $L|_{U}$ is non-redundant.
\end{proposition}
\begin{proof}[Sketch]
  $\Rightarrow$  
  We show the contrapositive: suppose $L|_{U}$ is redundant.
  Then there is a $r,r' \in \U$ such that $\Gamma_r \subseteq \Gamma_{r'}$.
  Then for all $p \in \Gamma_r$, we have $\{r, r'\} \subseteq \Gamma(p)$.
  Therefore, $\U \setminus \{r\}$ still a representative set, so $\U$ is not minimum.

  \btw{Commenting out other statements with FDLS- Jessie 1 June 21}
%  $(b \implies c)$
%  If $L|_\R$ is non-redundant, then for all $r \in \R$, there is no $r'$ so that $\Gamma_r \subseteq \Gamma_{r'}$.
%  This means the multiset $\{\Gamma_r : r \in \R\}$ contains no duplicate elements, since it has duplicate elements if and only if $\Gamma_r = \Gamma_{r'}$.
%  Moreover, each $\Gamma_r$ is full-dimensional, since if there was a $\Gamma_r$ that was lower dimensional, it would have to be a subset of another level set, which would contradict non-redundancy. \jessiet{Hand waving here}
%  Finally, we have $\cup_{r \in \R} \Gamma_r = \simplex$ since $\R$ is representative.
%  
%  $(c \implies a)$
%  As $\Gamma_r$ is full-dimensional and there are no $r, r' \in \R$ such that $\Gamma_r = \Gamma_{r'}$, for each $r \in \R$ there must be some distribution $p_r \in \simplex$ so that $\Gamma(p_r) = \{r\}$.
%  Thus, $\R \setminus \{r\}$ not a representative set for all $r \in \R$.
%  Therefore, $\R$ is minimum.

  $\Leftarrow$
  \btw{Commented out version relying on hyperplanes without power diagrams; it was incorrect - Jessie 1 June 21}
  Since $\U$ is a finite representative set, we know $L|_\U$ is embedded by $L$ nu Corollary~\ref{cor:representative-embeds-restriction}.
  Therefore, $\Gamma := \prop{L}$ embeds $\Gamma|_\U := \prop{L|_\U}$, and by assumption $\Gamma|_\U$ is non-redundant.
  By Proposition~\ref{prop:embed-trim}\jessiet{BTW: Forward ref}, $\U$ is a minimum representative set for $L$.
%  Since $\R^*$ is finite, it suffices to show that for all $r \in \R^*$, there exists some $p_r \in \simplex$ such that $\{r\} = \Gamma(p_r)$.
%  This implies the result, as removing $r$ from $\R^*$ would make $\Gamma(p_r) = \emptyset$, and therefore $\R^* \setminus \{r\}$ would not be representative.
%  
%  If there was an $r \in \R^*$ such that there was no such $p_r$, but $\Gamma_r \not \subseteq \Gamma_{r'}$ for any other $r' \in \R^*$, then we must have some $r', r''$ such that there exists a $p_{r'}^r$ and $p_{r''}^r$ such that $\{r,r'\} \subseteq \Gamma(p_{r'}^r)$ and $r'' \not \in p_{r'}^r$, and similarly, $\{r, r''\} \subseteq \Gamma(p_{r''}^r)$ and $r' \not \in \Gamma(p_{r''}^r)$.
%  
%  Observe that the hyperplane $H_L(p; u) := p \mapsto \inprod{p}{L(u)}$ supports $\risk{L}$ at $p$ if and only if $r \in \Gamma(p)$.
%  By assumption, we have $H_L(p_{r'}^r; r)$ supporting $\risk{L}(p_{r'}^r)$ and $H_L(p_{r''}^r; r)$ supporting $\risk{L}(p_{r''}^r)$.
%  As $H_L(\cdot;r)$ is linear in its first argument (this is true for any $r \in \R^*$), then $\risk{L}$ must be linear between $p_{r'}^r$ and $p_{r''}^r$.
%  
%  Now observe that 
%  $r' \in \Gamma(p_{r'}^r) \iff H_L(p_{r'}^r; r')$ supports $\risk{L}(p_{r'}^r)$.
%  Since $\risk{L}$ is linear between $p_{r'}^r$ and $p_{r''}^r$, \jessie{THIS IS INCORRECT} it therefore also supports $\risk{L}(p_{r''}^r) \iff r' \in \Gamma(p_{r''}^r)$, yielding a contradiction.
%  
%  Therefore, for all $r \in \R^*$, there must be some $p_r$ such that $\Gamma(p_r) = \{r\}$, and thus $\R^*$ is a minimum representative set.

@@

\begin{restatable}{proposition}{embedtrim}\label{prop:embed-trim}
	Let $\Gamma:\simplex\toto\reals^d$ be an elicitable property.
	The following are equivalent:
	\begin{enumerate}\setlength{\itemsep}{0pt}
		\item $\Gamma$ embeds a \jessie{nonredundant} finite property $\gamma:\simplex \toto \R$.
		\item $\trim(\Gamma)$ is a finite set, and $\cup\,\trim(\Gamma) = \simplex$.
		\item There is a finite minimum representative set $\U$ for $\Gamma$.
		\item There is a finite set of full-dimensional level sets $\Theta$ of $\Gamma$, and $\cup\,\Theta = \simplex$.
	\end{enumerate}
	% \raft{I see why you wanted this addition here, but (a) it's clear from the def of embedding, and (b) we don't have varphi defined.  So let's leave it out.}
	Moreover, when any of the above hold, $\trim(\gamma) = \trim(\Gamma) = \{\Gamma_u : u\in\U\} = \Theta$, and $\gamma$ is elicitable.
\end{restatable}
\begin{proof}
	Let $L$ elicit $\Gamma$.

	1 $\Rightarrow$ 2:
	% \jessie{Loss intuition: Let $L$ elicit $\Gamma$.  If $\Gamma$ embeds a finite $\gamma'$, $L$ must embed a discrete loss $\ell$ such that $\ell(r) = L(\varphi(r))$.  Therefore, $\risk{L} = \risk{\ell}$ is polyhedral. Moreover, we have $\Gamma$ also embedding the finite property $\prop{\ell} := \gamma$ as a corollary of the definition of embedding properties. We claim $\trim(\Gamma) = \{\gamma_r : r \in \R\}$ (Lemma~\ref{lem:embedded-level-sets-trim}), and since the latter set is finitely generated (as $\R$ is finite), we have have $\trim(\Gamma)$ is finite.  Moreover, as $\gamma$ is nondegenerate (since it is defined over the simplex), we have that $\cup_{r \in \R} \gamma_r = \simplex$.}
	If $\Gamma$ embeds a finite $\gamma$, then any representative set $\Sc \subseteq \R$ is finite, and so any minimum representative set is finite; $\trim$ is then finite as it is finitely generated.
	$\cup \trim(\Gamma) = \simplex$ follows from representativeness.

\btw{Commenting out 2 $\Rightarrow$ 1 for now since I added 1-> 2 -> 3 ->1 for cyclicity.}
%	\raft{These next two directions together seem like what we did before for $2\Rightarrow 3$, correct?  (Not as complete though; see the step where we justify the conditions of Lemma~\ref{lem:loss-restrict}.)  I'm actually happy for them to be separated, but let's make sure the argument is just as complete. \jessie{Added in the conditions of Lemma 3 to be a bit more thorough.}}\btw{Not sure how old this comment is, but feel free to burn if you're happy with thoroughness.}
%	2 $\Rightarrow$ 1:
%	As $\trim(\Gamma)$ is finite, we know $\trim(\Gamma) = \{\Gamma_{u_i} \mid u_i \in \U\}$ for some minimum representative set $\U$ of finite cardinality $k$.
%	Then we can apply Lemma~\ref{lem:loss-restrict} to observe that $L$ embeds $L|_\U$, and therefore $\Gamma$ embeds $\prop{\ell}$, which is finite as $\ell$ is discrete.

	2 $\Rightarrow$ 3: 
	Suppose $\trim(\Gamma) = \{\Gamma_u \mid u \in \U\}$.
	Then we know $\U$ is a minimum representative set, and since $\trim(\Gamma)$ is finite, so is $\U$; if it was not, then $\U$ would not be minimum.

	3 $\Rightarrow$ 1:
	Since $\U$ is representative, we have $\Gamma(p) \cap \U$ nonempty for all $p \in \simplex$, and therefore, $\Gamma$ embeds $\Gamma|_\U$, which is finite as $\U$ is finite.
	Since $\U$ is minimum, the constructed $\Gamma_\U$ is additionally non-redundant.

	1 $\Rightarrow$ 4:
%	Let $\varphi: \R \to \reals^d$ be the embedding function, and take $\Theta = \{\Gamma_{\varphi(r)} : r \in \R\}$.
%	The latter set is equal to $\{\gamma_r : r \in \R\}$ by Lemma~\ref{lem:embedded-level-sets-trim}.
%	Therefore, we know each $\theta \in \Theta = \gamma_r$ for some $r \in \R$, which is full-dimensional in the affine hull of the simplex.
%	Moreover, since $\gamma$ is non-degenerate, we have $\cup \Theta = \cup_r \gamma_r = \simplex$.	
	\btw{Previous version commented out above because it relies on old definitions - Jessie 1 June 21}
	Since $\Gamma$ embeds a finite property $\gamma$, we have a finite minimum representative set $\Sc$ for $\gamma$ such that $\{\Gamma_u \mid u \in \varphi(\Sc)\} = \{\gamma_r \mid r \in \Sc\}$.
	Take $\Theta = \trim(\Gamma)$; since $\U$ is representative, we know $\cup \Theta = \simplex$.
	Moreover, $\Theta$ is finite since $\Sc$ is finite.
	It is just left to show each $\theta \in \Theta$ is full-dimensional.
	Since $\gamma$ is a finite property, its level sets form a power diagram in the simplex (Theorem~\ref{thm:aurenhammer}).
	If there was a $\theta = \gamma_r$ that was not full-dimensional, it must therefore be the face of another level set.
	Since level sets of elicitable properties are closed, $\gamma_r$ must then be a face of some facet $\gamma_{r'}$.
	Therefore, $\gamma_r \subseteq \gamma_{r'}$, contradicting $\Sc$ being minimum, so each $\theta \in \Theta$ must be full-dimensional.

	%	\hrule
	%	Since $\Gamma$ embeds the finite property $\gamma$, Lemma~\ref{lem:embed-defs-equiv} yields a loss $\ell$ eliciting $\gamma$ embedded by $L$, and therefore $\risk{L} = \risk{\ell}$.
	%	As in the proof of Proposition~\ref{prop:embed-bayes-risks}, we observe that every facet of the epigraph of $-\risk{\ell}$ projects onto the simplex as a full-dimensional level set of $\gamma$.
	%	As the risks are equal, this is also true for $\Gamma$.
	%	Observe each cell in the simplex of $\gamma$ has some report $r$ so the cell is $\gamma_r$.
	%	If $\varphi: r \mapsto u_r$, then we must have $\gamma_r = \Gamma_{u_r}$.
	%	Take $\Theta$ to be the set $\{\Gamma_{u_r} : u_r \in \varphi(\R)\}$.
	%	We have shown each $\Gamma_{u_r}$ is full-dimensional, and as the union of these cells forms a power diagram on $\simplex$, we have $\cup \Theta = \simplex$.

	4 $\Rightarrow$ 1: \jessie{Intuition: Take $\gamma : p \mapsto \Gamma(p) \cap \varphi(\R)$.}
	Let $\Theta = \{\theta_1,\ldots,\theta_k\}$.
	For all $i\in\{1,\ldots,k\}$ let $u_i\in\reals^d$ such that $\Gamma_{u_i} = \theta_i$.
	Now define $\gamma:\simplex\toto\{1,\ldots,k\}$ by $\gamma(p) = \{i : p\in\theta_i\}$, which is non-degenerate as $\cup\,\Theta = \simplex$.
	By construction, we have $\gamma_i = \theta_i = \Gamma_{u_i}$ for all $i$, so letting $\varphi(i) = u_i$ we satisfy the definition of embedding, namely statement (i.).

\btw{Commenting out remark to be replaced by Prop~\ref{prop:embed-trim} - Jessie, 1 June 21}
%\begin{remark}\label{remark:embed-trim}
%  Let $\Gamma:\simplex\toto \R$ be an elicitable property.
%  The following are equivalent:
%  \begin{enumerate}\setlength{\itemsep}{0pt}
%  \item $\Gamma$ embeds a finite property $\gamma:\simplex \toto \R'$.
%  \item $\Gamma$ has a finite representative set $\U$.\jessie{, and therefore any minimum representative set for $\Gamma$ is also finite.}
%  \item There is a finite multiset $\Theta$ full-dimensional level sets of $\Gamma$, and $\cup\, \Theta = \simplex$. 
%  \end{enumerate}
%  Moreover, when $\Gamma$ tightly embeds $\gamma$, $\U$ is a minimum representative set, and there is a $\Theta' \subseteq \Theta$ with no duplicate elements such that $\cup \Theta' = \simplex$.
%\end{remark}
%\begin{proof}[Sketch]
%  $(a \implies b)$
%  If $\Gamma$ embeds $\gamma$, then we can take the embedded target reports $\U := \varphi(\R')$ and show this is a finite representative set for $L$.
%  We know it is finite as $\R'$ is finite, and consider that $\Gamma_{\varphi(r)} = \gamma_r$ for all $r \in \R'$, hence $\R \cap \gamma(p) \neq \emptyset \implies \varphi(\R) \cap \Gamma(p) \neq \emptyset$ for all $p \in \simplex$.	

@@

%  $(b \implies c)$
%  Consider that if $\U$ is a finite representative set for $L$, then $L$ has a finite minimum representative set $\U' \subseteq \U$.
%  We have $\Theta := \trim(\Gamma) = \{\Gamma_u \mid u \in \U'\}$.
%  This is finite as $\U'$ is finite, and unions to the simplex by $\U'$ being representative.
%  If there was a level set $\Gamma_u$ for some $u \in \varphi(\R')$ that was not full-dimensional, it would have to be a subset of some other level set $\Gamma_{u'}$, but this contradicts that $\U'$ is minimal. \jessie{Hand waving; make the argument you can't span relints of other level sets.}

@@

%  $(c \implies a)$ 
%  For each $\theta \in \Theta$, there is some $u \in \R$ so that $\theta = \Gamma_u$; take $\U'$ to be the set of such $u$s.
%  We can see $\R'$ is representative since $\cup_{u \in \R'} \Gamma_u = \cup \theta = \simplex$, and therefore we have the result by an analog of Corollary~\ref{cor:representative-embeds-restriction}.

@@

%  % tight version; commented out May 8, 2021
%  % $(a \implies b)$
%  % If $\Gamma$ tightly embeds $\gamma$, then we can take the embedded target reports $\U := \varphi(\R')$ and show this is a finite minimum representative set for $L$.
%  % We know it is finite as $\R'$ is finite, and consider that $\Gamma_{\varphi(r)} = \gamma_r$ for all $r \in \R'$.
%  % If $\U$ was not minimum, then there would be some $r \in \R'$ so that $\U \setminus \{\varphi(r)\}$ is still representative.
%  % This is true if and only if $\R' \setminus \{r\}$ is still representative for $\ell$, which contradicts non-redundancy of $\ell$ by tight embedding (Prop~\ref{prop:tfae-min-rep-nonredundant}).
%  % Therefore, $\U$ is a finite minimum representative set for $L$.

@@

%  % $(b \implies c)$
%  % We have $\trim(\Gamma) = \{\Gamma_u \mid u \in \varphi(\R')\}$, and take $\Theta := \trim(\Gamma)$.
%  % This is finite as $\varphi(\R')$ is finite, and unions to the simplex by $\varphi(\R')$ being representative.
%  % If there was a level set $\Gamma_u$ for some $u \in \varphi(\R')$ that was not full-dimensional, it would have to be a subset of some other level set $\Gamma_{u'}$, but this contradicts that $\varphi(\R')$ is minimal. \jessie{Hand waving; make the argument you can't span relints of other level sets.}

@@

%  % $(c \implies a)$ \jessie{Not quite: we need the multiset to have no duplicate elements}
%  %% If we show $ c \implies b$, we have $b \implies a$ as an version of Corollary~\ref{cor:representative-embeds-restriction}.
%  % For each $\theta \in \Theta$, there is some $u \in \R$ so that $\theta = \Gamma_u$; take $\R'$ to be the set of such $u$s.
%  % If $\R'$ is a minimum representative set, then we have the result by an analog of Corollary~\ref{cor:representative-embeds-restriction}.
%  % We can see $\R'$ is representative since $\cup_{u \in \R'} \Gamma_u = \cup \theta = \simplex$, and it is minimum since the multiset of $\Theta$ has no duplicate elements.
%  % As the level sets are full-dimensional, each level set $\Gamma_u$ has some $p_u$ such that $\Gamma(p_u) = \{u\}$, so removing any $u$ from $\R'$ would make $\R'$ not representative.	
%\end{proof}

%\bigskip
%\hrulefill
\btw{Moved a bunch of statements from here to the Appendix Jessie 1 June 21}
%
